### 2015-01-28 src/misc/s6_thanks.tex
Updated word of thanks

Second, I would like to thank \textbf{my family} Thaja, Annika, Sjors, Marcel, and Billy, Lancy, Percy, Stephanie, and Tyra, and \textbf{my friends in Boxtel \footnote{Including Lennisheuvel and Vught}} Kees, Paul, Bram, Joukje, Marieke, and Lieke.

>>>>

Second, I would like to thank \textbf{my family} Thaja, Annika, Sjors, Marcel, Senn, and Billy, Lancy, Percy, Stephanie, and Tyra, and \textbf{my friends in Boxtel \footnote{Including Lennisheuvel and Vught}} Kees, Paul, Bram, Joukje, Marieke, and Lieke.
